Turbulence in compact to giant HII regions

### 2022-01-04 strucfunc_paper.tex
Describe measurement and use of line moments in sec 2.1

%We use data from \citet{1987A&A...176..347H} and \citet{arthur2016turbulence} to study of turbulence in the Orion Nebula.
%\cite{1987A&A...176..347H} observations were obtained using a 106 cm-Cassegrain telescope at Observatorium Hoher List. 
%A Fabry-Pérot interferometer was used with a étalon a separation of 0.5 mm. 
%Interferograms have been taken with different pointing directions of the telescope's optical axis in the nebula. 
%The exposures are overlapped and fall into one square of a grid with a width of 1' centered at \(\theta^{1}\)Ori C.

Wherever possible, we calculate the centroid velocity directly as the first moment
of the line intensity profile for each position on the nebula.
So long as the signal-to-noise is high enough,
this mean velocity can be calculated to a much higher precision
than the nominal velocity resolution of the spectrograph. 
In a few cases, as noted below, we are working with already reduced data,
which are provided in the form of Gaussian fits to the line profiles.
In the cases where multiple Gaussian components have been fitted,
we take the flux-weighted mean velocity of these components to be the centroid.

@@

The second-order structure function of the velocity centroids, $B(r)$, is defined as:
%
\begin{equation}\label{eq:Br}
  B(\boldsymbol{r}) = \dfrac{1}{N(\boldsymbol{r})}
  \,
  \sum_{\text{pairs}} \bigl[
  V_{c}(\boldsymbol{x} + \boldsymbol{r}) - V_{c}(\boldsymbol{x})
  \bigr]^{2}
\end{equation}
%
where $N(\boldsymbol{r})$ is the number of pair points at each separation \(\boldsymbol{r}\), called lag. 
In the Kolmogorov model \(B(r) \propto r^{2/3}\).

The variance of the centroid velocity fluctuations is:
%
\begin{equation}\label{eq:variance}
\sigma^2  = \frac{1}{N} \sum_{\text{pixels}} \bigl[ V_c (\boldsymbol{x}) -\langle V_ c\rangle  \bigr]^2
\end{equation}
%
the, \(\langle V_c \rangle \) is the mean centroid velocity
%
\begin{equation}\label{eq:mean}
\langle V_c \rangle \  = \frac{1}{N} \sum_{\text{pixels}} V_c (\boldsymbol{x})
\end{equation}
%
The summation in Equation \ref{eq:Br} is over all data pairs for each separation \(N(\boldsymbol{r})\).
The summations in Equations \ref{eq:variance} and \ref{eq:mean} are over the total number of valid pixels in the (\textit{x},\textit{y})-plane.

@@

\begin{equation}\label{eq:Cr}
C(\boldsymbol{r}) = \dfrac{\sum_{\text{pairs}}[V_{c}(\boldsymbol{x} + \boldsymbol{r}) \times V_{c}(\boldsymbol{x}) ]} {N(\boldsymbol{r})}
\end{equation}
%
and is another statistical tool used in studying the turbulent flows.
The interpretation of the Equation \ref{eq:Cr} depends on the assumption of homogeneity, which may be violated for astrophysical processes.
Because of this, Equation \ref{eq:Br} is a better approach to characterize the velocity fluctuations even in the presence of large scale linear gradients and may be sensitive to a wider range of scales \citep{1984ApJ...277..556S}.

>>>>

%We use data from \citet{1987A&A...176..347H} and \citet{arthur2016turbulence} to study of turbulence in the Orion Nebula.
%\cite{1987A&A...176..347H} observations were obtained using a 106 cm-Cassegrain telescope at Observatorium Hoher List. 
%A Fabry-Pérot interferometer was used with a étalon a separation of 0.5 mm. 
%Interferograms have been taken with different pointing directions of the telescope's optical axis in the nebula. 
%The exposures are overlapped and fall into one square of a grid with a width of 1' centered at \(\theta^{1}\)Ori C.
\newcommand\xx{\ensuremath{\boldsymbol{x}}}
Wherever possible, we calculate the centroid velocity \(V_c\)
directly as the normalized first velocity moment of the spectral line intensity profile
for each plane-of-sky position \(\xx\) on the nebula:
\(V_{c}(\xx) = M_1(\xx) / M_0(\xx)\).
The \(k\)th unnormalized moment \(M_k\) of the continuum-subtracted
spectral intensity profile \(I(v)\)
is defined as
\begin{equation}
  \label{eq:kth-moment}
  M_k = \int_{\Delta v} I(v) \, v^k \, dv
\end{equation}
where the Doppler velocity \(v\) is calculated according to
the \texttt{VOPT} convention
\citetext{Eq.~[32] of \citealt{Greisen:2006a}}:
\begin{equation}
  \label{eq:optical-velocity}
  v \equiv c\, (\lambda - \lambda_0) / \lambda_0 ,
\end{equation}
where \(\lambda\) is the observed wavelength,
\(\lambda_0\) is the rest wavelength, and \(c\) is the speed of light.
The spectral window \(\Delta v\) is chosen to be just large enough to include
the entire \ha{} emission line.
So long as the signal-to-noise is high enough,
this mean velocity can be calculated to a much higher precision
than the nominal velocity resolution of the spectrograph. 
In a few cases, as noted below, we are working with already reduced data,
which are provided in the form of Gaussian fits to the line profiles.
In the cases where multiple Gaussian components have been fitted,
we take the flux-weighted mean velocity of these components to be the centroid.

The observed RMS spectral line width \(\sigma'\) can likewise be found from
the second velocity moment as
\begin{equation}
  \label{eq:observed-sigma}
  \sigma'(\xx)^2  = [M_2(\xx) / M_0(\xx)] - V_{c}(\xx)^2 .
\end{equation}
However, many different broadening mechanisms contribute to this width,
including the finite spectral resolution \(\sigma_{\mathrm{ins}}\),
fine-structure splitting \(\sigma_{\mathrm{fs}}\),
and thermal Doppler broadening \(\sigma_{\mathrm{t}}\).
In the approximation that all these broadening mechanisms are independent
and described by Gaussian profiles, then the dispersion of
line-of-sight velocities due to bulk motions \(\sigma\los\) can be found
by subtracting these contributions in quadrature from the observed width:
\begin{equation}
  \label{eq:sigma-los}
  \sigma\los^2 = \sigma'^2 - \sigma_{\mathrm{ins}}^2 - \sigma_{\mathrm{fs}}^2 - \sigma_{\mathrm{t}}^2 .
\end{equation}

@@

The second-order structure function of the velocity centroids, $B(r)$, is defined as:
%
\begin{equation}\label{eq:Br}
  B(\boldsymbol{r}) = \dfrac{1}{N(\boldsymbol{r})}
  \,
  \sum_{\text{pairs}} \bigl[
  V_{c}(\xx + \boldsymbol{r}) - V_{c}(\xx)
  \bigr]^{2}
\end{equation}
%
where $N(\boldsymbol{r})$ is the number of pair points at each separation \(\boldsymbol{r}\), called lag. 
In the Kolmogorov model \(B(r) \propto r^{2/3}\).

The variance of the centroid velocity fluctuations is:
%
\begin{equation}\label{eq:variance}
\sigma^2  = \frac{1}{N} \sum_{\text{pixels}} \bigl[ V_c (\xx) -\langle V_ c\rangle  \bigr]^2
\end{equation}
%
the, \(\langle V_c \rangle \) is the mean centroid velocity
%
\begin{equation}\label{eq:mean}
\langle V_c \rangle \  = \frac{1}{N} \sum_{\text{pixels}} V_c (\xx)
\end{equation}
%
The summation in Equation \ref{eq:Br} is over all data pairs for each separation \(N(\boldsymbol{r})\).
The summations in Equations \ref{eq:variance} and \ref{eq:mean} are over the total number of valid pixels in the (\textit{x},\textit{y})-plane.

@@

\begin{equation}\label{eq:Cr}
C(\boldsymbol{r}) = \dfrac{\sum_{\text{pairs}}[V_{c}(\xx + \boldsymbol{r}) \times V_{c}(\xx) ]} {N(\boldsymbol{r})}
\end{equation}
%
and is another statistical tool used in studying the turbulent flows.
The interpretation of the Equation \ref{eq:Cr} depends on the assumption of homogeneity, which may be violated for astrophysical processes.
Because of this, Equation \ref{eq:Br} is a better approach to characterize the velocity fluctuations even in the presence of large scale linear gradients and may be sensitive to a wider range of scales \citep{1984ApJ...277..556S}.
